---
title: "Writing Functions"
author: "Anna Ma"
date: "11/8/2021"
output: github_document
---

```{r, message=FALSE}
library(tidyverse)
library(rvest)
```

```{r}
set.seed(1)
```

## Z scores

```{r}
x_vec = rnorm(25, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)

z_scores = function(x){
  
  z = (x - mean(x)) / sd(x)
  
  return(z)
  
}

z_scores(x = x_vec)

y_vec = rnorm(40, mean = 12, sd = .3)

z_scores(y_vec)
#this will assume y_vec is the x in the function 
```

These will return error message for the above function

```{r, eval = FALSE}
z_scores(3)

z_scores(c("this","is","a","vector"))

mtcars

z_scores(mtcars)
```


```{r}
# ask the function to check if x fit some criteria
z_scores = function(x){
  
  if (!is.numeric(x)) {
    stop("x needs to be numeric") 
    }
  
  if (length(x) < 3) {
    stop("x should have at least 3 numbers")
  }
  
  z = (x - mean(x)) / sd(x)
  
  return(z)
  
}
```

## Multiple outputs

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  output_df = 
    tibble(mean = mean_x, 
       sd = sd_x)
  # or use list(mean = mean_x, sd = sd_x)
  return(output_df)
}
```

Verifying the function works

```{r}
mean_and_sd(y_vec)
```

## Multiple Inputs
### Different sample sizes, means, sds

```{r}
sim_data = 
  tibble(
    x = rnorm(30, mean = 2, sd = 3)
  )

sim_data %>% summarize(
  mean = mean(x),
  sd = sd(x)
)
```

Function that simulates data, computes the mean and sd.

```{r}
# the input suppose i want sample size n, true mean mu, and true standard deviation sigma
sim_mean_sd = function(n,mu,sigma){
  
  # do checks on inputs
  sim_data = 
    tibble(
      x = rnorm(n, mean = mu, sd = sigma)
    )
  
  sim_data %>% summarize(
    mean = mean(x),
    sd = sd(x)
  )  
  
}


sim_mean_sd(30,4,3)
```

Shift + option + put the cursor range, then the cursor gets repeated across multiple lines. Whatever u type in one, will be typed into the others as well. 

We can also set defults
```{r}
sim_mean_sd2 = function(n,mu = 3, sigma = 4){
  
  # do checks on inputs
  sim_data = 
    tibble(
      x = rnorm(n, mean = mu, sd = sigma)
    )
  
  sim_data %>% summarize(
    mean = mean(x),
    sd = sd(x)
  )  
  
}
sim_mean_sd2(30)
```

## Revisit Neapolitan Dynamite
The following code is from previous lectures

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = 
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
)
```

There are a lot of pages for reviews

So, we can write a function that gets reviews based on page url (page number)

```{r}
get_page_reviews = function(page_url){
  
  page_html = read_html(page_url)

  review_titles = 
    page_html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    page_html %>%
    html_nodes("#cm_cr-review_list   .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    page_html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()
  
  reviews = 
    tibble(
      title = review_titles,
      stars = review_stars,
      text = review_text
  )
  
  return(reviews)
}

url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

get_page_reviews(url)


url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2"

get_page_reviews(url)
```

```{r}
base_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

urls = str_c(base_url, 1:5)

get_page_reviews(urls[1])
```

