---
title: "Iteration and list columns"
author: "Anna Ma"
date: "11/13/2021"
output: github_document
---

```{r, message = FALSE}
library(tidyverse)
library(rvest)

set.seed(1)
```

## Define Function 

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  output_df = 
    tibble(mean = mean_x, 
       sd = sd_x)
  # or use list(mean = mean_x, sd = sd_x)
  return(output_df)
}
```

## Lists

```{r}
l = 
  list(
    vec_numeric = 5:8,
    vec_logical = c(TRUE, FALSE),
    summary = summary(rnorm(1000, mean = 5, sd = 3))
)

# 3 ways to access the third element of this list:

l[[3]]

l[["summary"]]

l$summary

```

## List of normals

```{r}
list_norms = 
  list(
    a = rnorm(50, mean = 2, sd = 1),
    b = rnorm(50, mean = 5, sd = 3),
    c = rnorm(50, mean = 20, sd = 1.2),
    d = rnorm(50, mean = -12, sd = 0.5)
  )
```

## Use function on list 

```{r}
#This uses the element sequence.
mean_and_sd(list_norms[[1]])
# or mean_and_sd(list_norms[["a"]]) this use name
```


## For loop

lets use a for loop to iterate over the list of normals. 

Steps to do it:
1. Identify the input. In this case, the input is the list of normals
2. Figure out the output. We want a vector that is a list and have 4 open spots. 
3. Know the function that we want to apply to the input
4. Use function on the input list and put the result into the output list

```{r, include = FALSE}
output = vector("list",length = 4)
# This creates a empty list with 4 spots

output[[1]] = mean_and_sd(list_norms[[1]])
# use mean and sd function on the first element in the in put list, and put the result as the first element in the out put list that we just created 
```

Now, we can use a for loop to iterate what we did on a single element to create a complete list for all the elements in the list. 

```{r}
for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}

output
```

Lets use map instead

```{r}
#map input on to the function and return output for all 
output_map = map(list_norms, mean_and_sd)

output_map

# same result with for loop

# we can also do 
map(list_norms, median)
map(list_norms, summary)
map(list_norms, IQR)
```

If we want to access element in the list, use: 
```{r}
output[[1]]
```

If we know the type of data that the output will be, we can do this an dget a simpler output. 

```{r}
map_dbl(list_norms, median)
```

## List Columns!!

```{r}
listcol_df = 
  tibble(
    name = c("a","b","c","d"),
    norms = list_norms
  )

#we can do any df stuff with this data frame, such as filter
listcol_df %>% 
  filter(name == "a")

listcol_df %>% pull(name)
listcol_df %>% pull(norms)

mean_and_sd(listcol_df$norms[[1]])

```


We can use map on the column of the data frame and use mutate to put all the result that we get from the map function into a new column of the original data frame! 

```{r}
listcol_df %>% 
  mutate(summaries = map(listcol_df$norms, mean_and_sd))
```


## Nested data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Nest data within location (nest into a sub dataframe)

```{r}
weather_nested = nest(weather_df, data = date:tmin)
 
# We can also do ... (shift+option to put cursor over multiple lines)
# weather_nested = 
#   weather_df %>% 
#   nest(data = date:tmin)


weather_nested %>% filter(name == "CentralPark_NY") %>% pull(data)

weather_nested$data[[1]]
```

Fit a regression

```{r}
lm(tmax ~ tmin, data = weather_nested$data[[1]])
```

Use a function for linear regression

```{r}
weather_lm = function(df){
  
  lm(tmax ~ tmin, data = df)
}

weather_lm(weather_nested$data[[1]])
```

Use the map function to apply linear regression to all the elements

```{r}
map(weather_nested$data, weather_lm)
```

Add the linear regression to the data frame we satrted with

```{r}
weather_nested %>% 
  mutate(lm_result = map(weather_nested$data, weather_lm))
```


## Unest

```{r}
unnest(weather_nested, data)

# weather_nested %>% unnest(data)
```

## Revisiting Napoleon

Function to get review / stars

```{r}
get_page_reviews = function(page_url){
  
  page_html = read_html(page_url)

  review_titles = 
    page_html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    page_html %>%
    html_nodes("#cm_cr-review_list   .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    page_html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()
  
  reviews = 
    tibble(
      title = review_titles,
      stars = review_stars,
      text = review_text
  )
  
  return(reviews)
}

base_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

urls = str_c(base_url, 1:5)
```

We will write, for the first element of this function, apply this... for the second element, do that... 

```{r}
map(urls, get_page_reviews)

napoleon_df = 
  tibble(
    urls = urls
    )

napoleon_df %>% 
  mutate(reviews = map(urls, get_page_reviews)) %>% 
  select(reviews) %>% 
  unnest()
``` 


